### 2018-02-26 FrascatiPlot/Paper/NucleiB2.tex
Adding abstract and table of contents

%\usepackage[utf8]{inputenc}

\usepackage[T1]{fontenc}

@@

\begin{document}
\begin{center}
{\Large {\bf Nuclei coalescence}}

@@

%
% Introduction 
%

\paragraph{Introduction.} 
The measured abundances of hadrons produced in heavy-ion collisions have been successfully described by statistical hadronization models over a wide range of energies~\cite{Andronic:2011yq,Cleymans:1998fq,Andronic:2005yp}. Thermal-statistical model calculations for central ultra-relativistic heavy-ion collisions are typically carried out in the grand-canonical ensemble. However, a grand-canonical description of particle production is only applicable if the volume $V=R^{3}$ of the system is large enough and as a rule of thumb one needs $VT^{3} > 1$ for a grand-canonical description to hold \cite{Hagedorn:1984uy,Rafelski:1980gk}. It must be noted, that this condition must be fulfilled for each conserved charge separately.
Several attempts were made to extend the picture of statistical hadronization to smaller systems such as pp or even e$^{+}$e$^{-}$ collisions~\cite{Redlich:2009xx,Becattini:1996gy,Kraus:2008fh}. While particle ratios of non-strange particles are observed to be very similar in small and large systems, the production of strangeness appears to be significantly suppressed in smaller systems. The data presented in~\cite{Adam:2016emw} shows for the first time, that there is a continuous increase of strangeness production with increasing event multiplicity across various collision systems. In the strangeness canonical approach, it is assumed that the total amount of strange hadrons in the volume is small with respect to non-strange hadrons. Thus the conservation of strangeness is guaranteed explicitly and not only on average while the bulk of the particles is still described in the grand-canonical ensemble. For further details on the this approach, we refer for instance to~\cite{BraunMunzinger:2003zd,BraunMunzinger:2001as,Hamieh:2000tk,Cleymans:2004bf,Kraus:2007hf}. The study presented here utilises the implementation in the THERMUS code~\cite{Wheaton:2004qb}.

>>>>

%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

\begin{document}
\begin{center}
{\Large {\bf Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei at LHC energies with recent and future Run 3 and 4 data}}

@@

%
% Introduction 
%
%\listoffigures
%\listoftables
%\newpage

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of 3He and hyper-tritons. Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our finding thus indicate the existence of a novel production mechanism for these objects.
\end{abstract}

\tableofcontents

\section{Introduction} 
The measured abundances of hadrons produced in heavy-ion collisions have been successfully described by statistical hadronization models over a wide range of energies~\cite{Andronic:2011yq,Cleymans:1998fq,Andronic:2005yp}. Thermal-statistical model calculations for central ultra-relativistic heavy-ion collisions are typically carried out in the grand-canonical ensemble. However, a grand-canonical description of particle production is only applicable if the volume $V=R^{3}$ of the system is large enough and as a rule of thumb one needs $VT^{3} > 1$ for a grand-canonical description to hold \cite{Hagedorn:1984uy,Rafelski:1980gk}. It must be noted, that this condition must be fulfilled for each conserved charge separately.
Several attempts were made to extend the picture of statistical hadronization to smaller systems such as pp or even e$^{+}$e$^{-}$ collisions~\cite{Redlich:2009xx,Becattini:1996gy,Kraus:2008fh}. While particle ratios of non-strange particles are observed to be very similar in small and large systems, the production of strangeness appears to be significantly suppressed in smaller systems. The data presented in~\cite{Adam:2016emw} shows for the first time, that there is a continuous increase of strangeness production with increasing event multiplicity across various collision systems. In the strangeness canonical approach, it is assumed that the total amount of strange hadrons in the volume is small with respect to non-strange hadrons. Thus the conservation of strangeness is guaranteed explicitly and not only on average while the bulk of the particles is still described in the grand-canonical ensemble. For further details on the this approach, we refer for instance to~\cite{BraunMunzinger:2003zd,BraunMunzinger:2001as,Hamieh:2000tk,Cleymans:2004bf,Kraus:2007hf}. The study presented here utilises the implementation in the THERMUS code~\cite{Wheaton:2004qb}.

\section{Coalescence approach}

\subsection{Source volume}

\section{Statistical-thermal approach and Blast-wave}

\section{Comparison with experimental data}

\subsection{(Anti-)nuclei with $A$ = 2, 3, 4}

\subsection{(Anti-)hyper-nuclei}

\section{Projections for the LHC Run 3 and 4}

\section{Summary and conclusions}
